\TheTitle

### 2017-07-11 paper/study.tex
Conceptual and summarization tasks
I think this covers most of the conceptual and summarization task
methodology.

The purpose of the study is to quantitatively and qualitatively evaluate
the effectiveness of \tool compared to the DAG-based visualizations
found in Gitk or the git command line. The study is broken into three
task-based sections; conceptual tasks, summarization tasks, and
participant opinions. The study was performed in June of 2017 in
Kingston ON, in a controlled environment running Ubuntu 14.04. When
conducting the study, participants were allowed to use both the git
command line and Gitk together, and \tool. We will refer to Gitk in the
study, but this includes the git command line, as we recognize that git
power-users may be more comfortable with the command line than a GUI.

@@

\dmg{use tasks, not questions. you are asking them to do something that requires an answer, that is different than a question}

@@

@@

\dmg{avoid editorializing your text: remove purely}

\dmg{watch for tense... we don't begin... the tasks begin... or better, the first tasks...}

The questions and tasks are broken down into four groups. The first two
groups are purely quantitative in nature; the study begins with
conceptual tasks to understand whether the DAG is capable of providing
users with an understanding of how a commit is merged into the master
branch, and other commits that it is merged with. We continue with
summarization tasks, to quantitatively understand if the \mt model makes
a difference in summarization tasks.

The third task set is purely qualitative, \dmg{and are their goal is ... don't imply content in your sentences... be
  precise; this applies to the paragraph before} to gain better understanding
of whether participants preferred working with the \mt model in \tool,
or working with the DAG in Gitk, and what aspects they preferred from
each tool. The final group of questions is simply to gain a better
understanding of the demographic of our participants.

\textbf{Conceptual Tasks}

\dmg{given the choice, not allowed.  I don't understand this section.
  You need to be more top-down in your description. you need to provide
  context on what the users are expected to do, and why. So what are the
  tasks? You never explain.  what is the goal of the tasks? how many?
  what were the tasks? what is expected from each? you need to answer
  these questions, not necessarily in the same order.  also, remember
  this is a comparative study, so I presume the users were asked to do
  both with linvis and without it (choice of gitk/git command line) }

% TODO: Move to methodology
The participants were given the choice of Gitk or the git command line
tools to perform the tasks .

The participants were allowed to use Gitk or the git command line tools
to perform these tasks. These tasks are asked in the specified order,
allowing tabularr to first, create a conceptual understanding of the
commits and merges that will be involved with the rest of the tasks that
follow.tabularmay then use their diagrams to answer T2 and T3. We do not
collect metrics from \tool for the conceptual tasks, opting instead to
determine if the DAG is sufficient for understanding how a commit is
integrated. \tool uses the \mt model show a tree visualization of how
commits are merged, until the commit reaches the master branch.
Table~\ref{tab:conceptual_tasks} shows the conceptual tasks.

\dmg{I don't like the present tense, but that is your option}

We provide the participant with 10 minutes per commit to complete the
first task. The answers to the two other questions in this section are
drawn from the answer in the first task.

\textbf{Summarization Tasks}

\dmg{again, you are going into details first. First the tasks --see
  above-- including their grouping.  then at the end, describe the
  randomization and why it is done (which you did) }

The summarization tasks (Table~\ref{tab:summarization_tasks}) are
grouped into \dmg{how many?} set of tasks according to their theme. The
tasks within a given task set are shuffled, and the task sets are
shuffled, to ensure that similar questions are together, but not in the
same order, and to ensure that the themes are in randomized order
between participants. The order of the commits is shuffled, as well. The
order of the tool is randomized, choosing to start with either \tool or
Gitk, to ensure that we do not place a bias on one tool through the
experiment.

As understanding where the merge begins and ends is vital to answering
the other question, the merge task set will always be the first task set
presented; however, the questions will still be re-ordered within the
task set.

@@

\dmg{this is still methodology.}
% TODO: Move to methodology
We recorded the audio and screen capture video for each participant in
the study for further analysis.
\dmg{you don't need this sentence, it is redundant}
After capturing the information, we
extracted various metrics from the videos.
\dmg{ you don't record, you measure}
From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy.

The correctness metric measures whether the answer was correct or
incorrect.

The accuracy metric measures the distance from the correct
answer. In task T4, the merges are important, and the order of those
merges is important to the answer. For this task, we use the edit
distance, which will increment if adding merges, removing merges, and
changing the order of the merges is necessary. T5 only asks for the set
of commits, so the order is not important, but the distance will
increase if adding or removing commits is necessary for getting the
correct answer. In T6 and T8 the answer is a single number, so the
distance is simply the difference between the answer provided and the
correct answer. In T7, there is only a single answer that is correct, so
the correctness metric and accuracy are the same, for this reason we do
not measure the accuracy of this task. The answer for T9 is similar in
requirements to T5, only asking for the set of files that had the most
changes. We use the same distance function in T9 and T10 as we did in
T5, measuring the number of items that must be added and removed from
the answer in order to change the response into the correct answer. % TODO: reword
T9 appears to be similar to T7 in that there is only a single file name
that must be provided, but in \comA, two files are modified the same
amount and are both the correct answer. In order to provide the correct
answer, the participant must be able to identify both files. In all
means of accuracy measurement, a correct answer will have a distance of
zero, while a non-zero distance indicates an incorrect answer.

The timing metric is measured from the video. We begin timing the task
at the end of the question, and stop timing before the last modification
to the answer. For this reason, it is possible for times to overlap
between tasks if the participant changes their answer after answering
another question. This will also modify the answer used for measuring
the accuracy.

>>>>

The purpose of the study is to quantitatively and qualitatively evaluate
the effectiveness of \tool compared to the DAG-based visualizations
found in Gitk or the git command line. The study is broken into three
task-based sections; conceptual tasks, summarization tasks, and
participant opinions. The study was performed in June of 2017 in
Kingston ON, in a controlled environment running Ubuntu 14.04.
Participants were allowed to use both Gitk and the git command line
tools together, which we will refer to as the git tools. Then they were
asked to perform the same tasks using \tool.

@@

% \dmg{use tasks, not questions. you are asking them to do something that requires an answer, that is different than a question}

The conceptual tasks are designed to gain better insight on the
comprehension of the DAG, and determine if the DAG is sufficient for
understanding what other commits are related to a given commit, and how
those commits are merged. The tasks are outlined in
Table~\ref{tab:conceptual_tasks}. The tasks are performed in order
using the git tools. T1 has the participant draw a diagram of the merge
tree, which will be used to answer the other two questions. This enables
us to visually see issues with comprehending the DAG visualizations.
Participants are given 10 minutes to perform this task, which also is
used to familiarize the participant with the git tools interface, if
they are not already, and with the set of commits they will be working
with. T2 and T3 are drawn directly from the diagram from T1, giving
quantitative metrics to measure the comprehension. T2 asks the
participant to verify the number of commits, and T3 asks for the number
of merges. The three tasks are performed on both commits before
continuing to the summarization tasks.

@@

The summarization tasks, listed in Table~\ref{tab:summarization_tasks},
are designed to compare the ability of the participants to summarize
information about the two commits used in the study when using git tools
verses \tool. The tasks are broken into four sets based on what is being
summarized: merges, authorship, files, and modules. The order that the
participants perform each task is randomized within each task set, and
the order of the task sets are then randomized with the exception of the
merges task set which will always come first. We measure and evaluate
three metrics for each task: correctness, accuracy, and timing.
Correctness measures whether the answer was correct or incorrect.
Accuracy measures how far from being correct the provided answer was.
Timing is the duration, in seconds, that the participant took to answer
the task. We begin timing the task at the end of the question, and stop
timing before the last modification to the answer. For this reason, it
is possible for times to overlap between tasks if the participant
changes their answer after answering another question. This will also
modify the answer used for measuring the accuracy. We measure the timing
from the screen capture.

\evan{Is this better, or do you still want me to move the information
  about the randomization to the bottom?}

@@

While the merge task set is part of the summarization task group, it
works less with the summarization of the commits and more with
comprehension of the models. The task is designed with two goals in
mind; first we want to measure and define which commits and which merges
the participant has defined to be in the merge tree; second to help
solidify which commits and merges will be used in the merge tree.

T4 provides a concrete series of merges that the participant believes to
be integrating the commit into the repository. T5 provides a concrete
set of commits that are related to the commit. We place these tasks
first as the answers to these will be necessary for the participant to
answer the tasks that follow, specifically finding the merge into the
master branch. T6 and T7 are related to the authorship at merges,
determining how many authors are involved and who made the most changes.
T8 and T9 are related to the files that were modified in the merge,
determining how many files were modified and which file had the most
changes. T10 is related to the modules that were modified in the merge.
Modules are not explicitly defined in git, but are a property of the
Linux repository that we noticed while looking at various commits. To
find the modules, take the text up to the first colon in the git log
preview. For the log preview \textit{``ALSA: kernel docs: fix
  sound/core/ kernel-doc''} the module is \textit{``ALSA''}, e.g.

The accuracy metrics are measured slightly differently between tasks due
to different requirements and structures in the answer. In task T4, both
the order and the merges are important. We define the distance to be the
edit distance with insertion, deletion, and transposition at unit cost.
The accuracy is the minimum edit distance necessary to make the answer
correct. T5, T9, and T10 are concerned with the set of elements in the
response; the order is not important. We use the Levenshtein distance,
with insertion, deletion, and substitution of unit cost, from the
provided answer to the correct answer. The answers to T6 and T8 are
single number values; the distance is measured as the absolute value of
the difference between the provided answer and the correct answer. T7
has only a single correct answer, thus the distance would either be zero
or one. For this reason, it is acceptable to omit the accuracy metric
from this task. The correctness metric is simply whether the answer was
correct or not; an accuracy of zero indicates a correct answer.

@@

\dmg{this is still methodology.}
% TODO: Move to methodology
% We recorded the audio and screen capture video for each participant in
% the study for further analysis.
% \dmg{you don't need this sentence, it is redundant}
% After capturing the information, we
% extracted various metrics from the videos.
% \dmg{ you don't record, you measure}
% From the conceptual tasks, we
% recorded the time in seconds, and the answer for the question. We
% extracted three metrics for the summarization tasks, the time in
% seconds, the correctness, and the accuracy.

In task T4, the merges are important, and the order of those
merges is important to the answer. For this task, we use the edit
distance, which will increment if adding merges, removing merges, and
changing the order of the merges is necessary. T5 only asks for the set
of commits, so the order is not important, but the distance will
increase if adding or removing commits is necessary for getting the
correct answer. In T6 and T8 the answer is a single number, so the
distance is simply the difference between the answer provided and the
correct answer. In T7, there is only a single answer that is correct, so
the correctness metric and accuracy are the same, for this reason we do
not measure the accuracy of this task. The answer for T9 is similar in
requirements to T5, only asking for the set of files that had the most
changes. We use the same distance function in T9 and T10 as we did in
T5, measuring the number of items that must be added and removed from
the answer in order to change the response into the correct answer. % TODO: reword
T9 appears to be similar to T7 in that there is only a single file name
that must be provided, but in \comA, two files are modified the same
amount and are both the correct answer. In order to provide the correct
answer, the participant must be able to identify both files. In all
means of accuracy measurement, a correct answer will have a distance of
zero, while a non-zero distance indicates an incorrect answer.
